Proving linearizability using forward simulations\thanks{An extended version of this paper including the missing proofs can be found at \cite{extended}.}

### 2017-05-05 draftCAV/queue.tex
Syntax of abstract state machines.

\begin{minipage}[t]{7.5cm}
\vspace{-3mm}
\begin{lstlisting}
function $\mathsf{present}$: $\mathbb{O} \to \mathbb{B}$
function $\mathsf{pending}$: $\mathbb{O} \to \mathbb{B}$
function $\mathsf{arg}$: $\mathbb{O} \to \mathbb{V}$
function $\mathsf{before}$: $\mathbb{O} \times \mathbb{O} \to \mathbb{B}$

rule inv(enq,v):
  let k = new $\mathbb{O}$
  $\mathsf{present}$(k) := true
  $\mathsf{pending}$(k) := true
  $\mathsf{arg}$(k) := v
  forall k' with $\mathsf{present}$(k')$\land \neg \mathsf{pending}$(k'):
    $\mathsf{before}$(k',k) := true

@@

rule ret(enq,v):
  let k with $\mathsf{arg}$(k) = v
  $\mathsf{pending}$(k) := false

@@

rule lin(deq,v):
  if v = EMPTY:
    forall k with $\mathsf{present}$(k):
      assert $\mathsf{pending}$(k)
  else:
    assert $\mathsf{present}$(k)
    let k with $\mathsf{arg}$(k) = v
    forall k' with $\mathsf{present}$(k'):
      assert $\lnot\mathsf{before}$(k', k)
    $\mathsf{present}$(k) := false

>>>>

\begin{minipage}[t]{7.5cm}
\vspace{-3mm}
\begin{lstlisting}
function present: $\mathbb{O} \to \mathbb{B}$
function pending: $\mathbb{O} \to \mathbb{B}$
function arg: $\mathbb{O} \to \mathbb{V}$
function before: $\mathbb{O} \times \mathbb{O} \to \mathbb{B}$

rule inv(enq,v):
  let k = new $\mathbb{O}$
  present(k) := true
  pending(k) := true
  arg(k) := v
  forall k' with present(k')$\land \lnot$pending(k'):
    before(k',k) := true

@@

rule ret(enq,v):
  let k with arg(k) = v
  pending(k) := false

@@

rule lin(deq,v):
  if v = EMPTY:
    forall k with present(k):
      assert pending(k)
  else:
    assert present(k)
    let k with arg(k) = v
    forall k' with present(k'):
      assert $\lnot$before(k', k)
    present(k) := false
